\section*{Requirements}

Two separate networks are required, one in Stockholm and one in London. These are to be connected over the insecure internet in a secure manner, meaning no information is exposed to any outsiders, no information is lost and it is not possible for any outsider to insert false information.

Wired connection to the network at each office is required and only accessible using company desktop workstations. These can not be used by unauthorized personnel.

Wireless connections to the networks at each office is required as well. Wireless connection will only be possible using company supplied laptops and company supplied mobile phones with authentication of users using digital identities and certificates. Employees from Stockholm visiting in London shall be able to access the Stockholm network using their company supplied laptops on the London wireless network.

It shall be possible to transfer files between two company supplied mobile phones in a secure manner. It shall not be possible to transfer a file from an employee to a non-employee.

\subsubsection*{Specifics to Stockholm office}

There shall be an intrusion detection system (IDS) deployed in the Stockholm network, monitoring traffic in the network and raising an alarm if an intrusion is detected as well as logging information about the intrusion.

A web server with access to company data shall be accessible to company employees from outside the network (e.g. from home with a private computer), only by using two factor authentication. This authentication must be performed using an application on the company supplied mobile phone. All traffic to and from this server shall be logged.

Finally, the complete security solution presented shall be scalable to accommodate for further expansions of the company's IT infrastructure.


